Selection coefficients at the phylogenetic and population-genetic scale

### 2022-05-16 manuscript/main.tex
Ancestral reconstruction with codon models

    \begin{abstract}
        Evidence for positive selection occurring in protein-coding DNA sequence is widespread across different taxa.
        Positive selection can be a result of adaptive evolution, meaning that individuals have had to adapt to a change in environment or selective pressure.
        However, current positive selection can also be the result of mutations compensating for deleterious substitutions that have accumulated along lineages, in which case positive selection is non-adaptive and predictable.
        To evaluate the extent of non-adaptive positive selection, we have combined population genetics and phylogenetic datasets.
        We first leveraged phylogenetic codon models which are based on a population-genetics formalism, assuming a non-adaptive fitness landscape.
        These models estimate the fitness of each of the 20 amino acids for each protein site, given mammalian protein-coding DNA alignments and gene tree topologies.
        Second, we integrated mammalian divergence data with polymorphic variants found in 29 populations across 7 mammalian genera.
        For each non-synonymous variant observed at the population level, we predicted its change in fitness from amino-acid fitness estimated at the mammalian scale.
        We found that a large proportion of observed non-synonymous changes are predicted to be positively selected, meaning that the ancestral allele is suboptimal.
        These supposedly advantageous variants are indeed showing signs of recent positive selection in all populations.
        Our work confirms that deleterious substitutions have accumulated across the phylogeny and are currently being compensated for, resulting in widespread positive selection that is not adaptive evolution.
        This study also shows the leverage obtained by integrating phylogenetic and population genetics on a common formalism.
    \end{abstract}

@@

    We usually say that a mutation is undergoing positive selection when it brings a fitness advantage to its bearer, and thus facilitate its own transmission to the next generation.
    However, the causes of this advantage can be diverse.
    We can distinguish two main advantages.
    The first advantage allows its bearer to become better adapted to a new or a changing environment, what we typically call adaptive evolution.
    The population as a whole is thus climbing the fitness landscape along an adaptive walk\cite{tenaillon_utility_2014}.
    The second is non-adaptive, in the sense that the increase in fitness of a new mutation is not a response to a new or a changing environment.
    Instead, the mutation restores the ancestral state which corresponded to an optimal functioning of the individual in a constant environment, but has been lost due to the fixation of a deleterious mutation by drift.
    The population as a whole is thus merely staying in the same position in fitness landscape at this equilibrium, and positive selection compensates for deleterious mutations that reach fixation due to drift\cite{sella_application_2005, mustonen_fitness_2009}.
    These two different kinds of selection result in a positive transmission bias of the advantageous allele, but their consequences are conceptually different.
    While adaptive evolution promotes phenotype diversification, non-adaptive positive selection promotes phenotype stability and preserves well established biological systems.
    It is thus of importance to be able to distinguish those two kinds of positive selection in order to understand the diversification of species.

    Inside proteins, positive selection can be quantified by comparing sequence variation inside a population with the sequence divergence with a sister species\cite{mcdonald_adaptative_1991}.

@@

    It's application across many taxa has uncovered that a large proportion of substitutions are positively selected\cite{moutinho_variation_2019}.

@@

    One of the most used methods to make these predictions is SIFT (Sort Intolerant From Tolerant) which reliably detects deleterious mutations in many taxa\cite{ng_sift_2003, vaser_sift_2016}.

@@

    In the other hand, at the DNA level, so-called mutation-selection codon models are rooted with population genetics formalism\cite{halpern_evolutionary_1998, mccandlish_modeling_2014}.

@@

    These models have been used as a null model to predict the overall rate of evolution of proteins\cite{spielman_relationship_2015, dosreis_how_2015}.
    A departure from this model indicates that proteins are evolving under a changing fitness landscape\cite{rodrigue_detecting_2017, tamuri_mutationselection_2021} and is a signal of adaptive evolution\cite{rodrigue_bayesian_2021}.
    In this study we want to address three main questions: which proportions of the polymorphism we observe in mammals is undergoing non-adaptive positive selection ?
    Are these mutations actually under positive selection at the scale of populations ?
    How does effective population size modulates positive, negative and weak selection ?

    \begin{figure*}[!ht]
        \
        \centering
        \includegraphics[width=\textwidth, page=1] {artworks/figure1}
        \caption{
            Integrating divergence and polymorphism for the detection of adaptation.
            At the phylogenetic level (panel A), amino-acid Wrightian fitness for each site are estimated from protein-coding DNA alignments using mutation-selection codon models.
            At the population-genetic level (panel B), for each observed single nucleotide polymorphism (SNP), selection coefficient are computed as the difference in amino-acid fitness between the ancestral and derived variant.
        }
        \label{fig:method}
    \end{figure*}

@@

    We replicated such experiment across 29 populations (fig.~\ref{fig:all-pop-results}), and found that mutations predicted to be deleterious are indeed purged at the population-genetic scale (blue and green rows in fig.~\ref{fig:all-pop-results}A).
    However, mutation predicted to be weakly advantageous ($\divWeakAdv$) are composed of a mix of neutral and selected mutations with varying proportions across the different populations (orange row in fig.~\ref{fig:all-pop-results}B).
    Similarly, mutations predicted to be advantageous are found to be positively selected with varying proportions (red row in fig.~\ref{fig:all-pop-results}C).
    A variable which could explain those variations between populations is the effective number of individuals in the population ($\Ne$), a major driver of selection efficacy.
    $\Ne$ is not directly accessible, and a reasonable proxy usually used is the synonymous diversity ($\theta=4\Ne\mu$ with $\mu$ the mutation rate).
    We thus ordered populations by increased synonymous diversity (fig.~\ref{fig:selcoeff-pop-phylo}A), exhibiting a decreased proportion of neutral mutations.
    This result suggest that populations with higher diversity (e.g.~\textit{Bos} or \textit{Ovis}) are more likely to discriminate whether mutations are advantageous or deleterious.
    Alternatively stated, mutations in populations with low diversity (e.g.~\textit{Homo}) are effectively nearly-neutral and behave as would a neutral mutation.
    This result is qualitatively in accordance with the nearly-neutral theory of evolution that mutations are less efficiently selected for small populations.
    Moreover, we found this effect to be in the same direction but less pronounced when we focused on all SNPs (fig.~S1) rather than only the SNPs predicted to be weakly selected (fig.~S2-3).
    To look further into the relation between diversity and selection efficacy, we thus studied the estimation of the mean $\SpopMean$ as a function of the mean $\SphyMean$ for a subset of SNPs, for which $\SphyMean$ is close to $0$.
    Indeed, polyDFE is a nearly neutral model and is not able to reliably compute selection coefficients for only strongly deleterious or only strongly advantageous SNPs.
    Sliding window of groups of $5.000$ SNPs are taken with a mean $\SphyMean$ between $-0.5$ and $0.5$ (fig.~\ref{fig:selcoeff-pop-phylo}B).
    $\SpopMean$ is estimated for each group, with some groups that might have part of same SNPs that overlap.
    The relationship between $\SpopMean$ and $\SphyMean$ is described as a second-order polynomial, and the slope of this polynomial at $\SphyMean=0$ gives the ratio $\SpopMean/\SphyMean$ for each population.
    We observe that $\SpopMean/\SphyMean$, representing the efficacy of selection at the short versus long-term is positively correlated with synonymous diversity (fig.~\ref{fig:selcoeff-pop-phylo}C), a proxy of effective population size.
    Altogether, populations with large effective population size are under more efficient selection, confirming the prediction of the nearly-neutral theory of evolution.

    As a consequence of increased selection efficacy, mutations in populations with high diversity are mechanically more likely to be deleterious (fig.~S4), especially for mutations predicted already to be deleterious at the phylogenetic scale (fig.~S5-6).
    However, and surprisingly, a decrease in the proportion of neutral mutation did not translate into a mechanical increase in the proportion of advantageous mutations.
    Instead, populations with higher diversity have a lower proportion of advantageous mutations (fig.~S7), this effect is also more pronounced for mutations predicted to be advantageous at the phylogenetic scale (red row in fig.~\ref{fig:all-pop-results}C and fig.~S8).
    This discrepancy can be explained by the fact that populations with larger diversity have already depleted the putatively advantageous mutations, and that only deleterious are remaining possible.
    In other words, being on the top of a fixed fitness landscape leaves you with only paths going downhill.
    Altogether, populations with increased diversity are showing signature of increased selection efficiency and are also less likely to generate positively selected mutations.

@@

    From a structural biology perspective, we found that proteins are not optimal, with a large proportion of mutations still toward more optimal amino acids.
    Seen from another angle, it means that we could theoretically derive the fittest proteins using only the amino acid with the highest fitness.
    Another way to confirm our predictions on amino acid fitness would be to test whether fittest proteins are also thermodynamically more stable, leveraging recent developments able to compute efficiently and accurately the folding of proteins.

@@

    Aside from methodological limitations, the mammalian case study might also not be representative of other clades.
    Indeed, our dataset is quite convenient because of relatively small population sizes since a large amount of deleterious mutations are fixed, and thus, there is a lot of opportunities for non-adaptive positive selection to arise.
    It would thus be of great interest to reproduce our experiment with other clades, such as \textit{drosophila} or birds which have higher effective population size.
    It would also be interesting to have access to more shallow but wider phylogenies to increase the resolution of our predictions.
    % Moreover, mammalian are less affected by codon usage

>>>>

    \begin{abstract}
        Evidence for positive selection occurring in protein-coding DNA sequence is widespread across different taxa.
        Positive selection can be a result of adaptive evolution, meaning that individuals have had to adapt to a change in environment or selective pressure.
        However, recent positive selection can also be the result of mutations compensating for deleterious substitutions that have accumulated along lineages, in which case positive selection is non-adaptive.
        To evaluate the extent of non-adaptive positive selection, we have combined population genetics and phylogenetic datasets.
        We first leveraged phylogenetic codon models which are based on a population-genetics formalism, assuming a non-adaptive fitness landscape.
        These models estimate the fitness of each of the 20 amino acids for each protein site, given mammalian protein-coding DNA alignments and gene tree topologies.
        Second, we integrated mammalian divergence data with polymorphic variants found in 29 populations across 7 mammalian genera.
        For each non-synonymous variant observed at the population level, we predicted its change in fitness from amino-acid fitnesses estimated at the mammalian scale.
        We found that a large proportion of observed non-synonymous changes are predicted to be positively selected, meaning that the ancestral allele is suboptimal.
        These supposedly advantageous variants are indeed showing signs of recent positive selection in all populations.
        Our work confirms that deleterious substitutions have accumulated across the phylogeny and are currently being compensated for, resulting in widespread positive selection that is not adaptive evolution.
        This study also shows the leverage obtained by integrating phylogenetic and population genetics on a common formalism.
    \end{abstract}

@@

    We usually say that a mutation is undergoing positive selection when it brings a fitness advantage to its bearer, and thus facilitate its own transmission to the next generation.
    However, the causes of this advantage can be diverse.
    We can distinguish two main scenarios in which a mutation is advantageous.
    The first scenario concerns environmental change.
    The bearer of the mutation that is advantageous in a new environment will be better adapted. Hence, its chances of survival and reproduction will be higher.
    This process is typically referred to as adaptive evolution.
    The second scenario involves the fixation of a deleterious mutation by drift, in which case the mutation restores the ancestral state which corresponded to an optimal state of the individual.
    This process is non-adaptive, in the sense that the increase in fitness of the new mutation is not in response to a new or a changing environment.
    Instead, the mutation restores the ancestral state which corresponded to an optimal functioning of the individual in a constant environment, but has been lost due to the fixation of a deleterious mutation by drift.
    Regarding the difference between these two scenarios at the population scale, while in the case of environmental change, the population as a whole is climbing the fitness landscape along an adaptive walk\cite{tenaillon_utility_2014}, in the case of
    non-adaptive positive selection, the population as a whole is thus merely staying in the same position in fitness landscape at this equilibrium, and positive selection compensates for deleterious mutations that reach fixation due to drift\cite{sella_application_2005, mustonen_fitness_2009}.
    These two different kinds of selection result in a positive transmission bias of the advantageous allele, but their consequences are conceptually different.
    While adaptive evolution promotes phenotype diversification, non-adaptive positive selection promotes phenotype stability and preserves well established biological systems.
    It is thus of importance to be able to distinguish those two kinds of positive selection in order to understand the diversification of species.

    Positive selection can be quantified by comparing sequence variation inside a population with the sequence divergence with a sister species\cite{mcdonald_adaptative_1991}.

@@

    It's application across many taxa has uncovered widespread positive selection\cite{moutinho_variation_2019}.

@@

    One of the most used methods to make these predictions is SIFT (Sort Intolerant From Tolerant), which reliably detects deleterious mutations in many taxa\cite{ng_sift_2003, vaser_sift_2016}.

@@

    At a finer scale, modelling at the codon level can disentangle processes of mutation at the DNA level and selection at the amino-acid level.
    For example, so-called mutation-selection codon models are rooted with population genetics formalism\cite{halpern_evolutionary_1998, mccandlish_modeling_2014}.

@@

    As a consequence, by integrating datasets at the species and population level, we can estimate the selection coefficient for each mutation currently segregating in a population.
    Such dataset can allow us to address different questions regarding positive selection affecting protein-coding DNA sequences.
    Which proportion of the segregating polymorphism are predicted to be positively selected, from a suboptimal to a more optimal amino acid?
    Are these polymorphism actually under ongoing positive selection at the scale of populations?
    How does effective population size modulates positive, negative and weak selection?
    Finally, how much of the recent substitutions are due to non-adaptive positive selection?

    \begin{figure*}[!ht]\
    \centering
    \includegraphics[width=\textwidth, page=1] {artworks/figure1}
    \caption{
        Integrating divergence and polymorphism.
        At the phylogenetic level (panel A), amino-acid Wrightian fitness for each site are estimated from protein-coding DNA alignments using mutation-selection codon models.
        At the population-genetic level (panel B), for each observed single nucleotide polymorphism (SNP) segregating in the population, selection coefficient are computed as the difference in amino-acid fitness between the ancestral and derived variant.
    }
    \label{fig:method}
    \end{figure*}

@@

    We replicated such experiment across 29 populations (fig.~\ref{fig:all-pop-results}), and found that mutations predicted to be deleterious are indeed purged at the population-genetic scale (blue and green rows in fig.~\ref{fig:all-pop-results}A).
    However, mutation predicted to be weakly advantageous ($\divWeakAdv$) are composed of a mix of neutral and selected mutations with varying proportions across the different populations (orange row in fig.~\ref{fig:all-pop-results}B).
    Similarly, mutations predicted to be advantageous are found to be positively selected with varying proportions (red row in fig.~\ref{fig:all-pop-results}C).
    A variable which could explain those variations between populations is the effective number of individuals in the population ($\Ne$), a major driver of selection efficacy.
    $\Ne$ is not directly accessible, and a reasonable proxy usually used is the synonymous diversity ($\theta=4\Ne\mu$ with $\mu$ the mutation rate).
    We thus ordered populations by increased synonymous diversity (fig.~\ref{fig:selcoeff-pop-phylo}A), exhibiting a decreased proportion of neutral mutations.
    This result suggest that populations with higher diversity (e.g.~\textit{Bos} or \textit{Ovis}) are more likely to discriminate whether mutations are advantageous or deleterious.
    Alternatively stated, mutations in populations with low diversity (e.g.~\textit{Homo}) are effectively nearly-neutral and behave as would a neutral mutation.
    This result is qualitatively in accordance with the nearly-neutral theory of evolution that mutations are less efficiently selected for small populations.
    Moreover, we found this effect to be in the same direction but less pronounced when we focused on all SNPs (fig.~S1) rather than only the SNPs predicted to be weakly selected (fig.~S2-3).
    To look further into the relation between diversity and selection efficacy, we thus studied the estimation of the mean $\SpopMean$ as a function of the mean $\SphyMean$ for a subset of SNPs, for which $\SphyMean$ is close to $0$.
    Indeed, polyDFE is a nearly neutral model and is not able to reliably compute selection coefficients for only strongly deleterious or only strongly advantageous SNPs.
    Sliding window of groups of $5.000$ SNPs are taken with a mean $\SphyMean$ between $-0.5$ and $0.5$ (fig.~\ref{fig:selcoeff-pop-phylo}B).
    $\SpopMean$ is estimated for each group, with some groups that might have part of same SNPs that overlap.
    The relationship between $\SpopMean$ and $\SphyMean$ is described as a second-order polynomial, and the slope of this polynomial at $\SphyMean=0$ gives the ratio $\SpopMean/\SphyMean$ for each population.
    We observe that $\SpopMean/\SphyMean$, representing the efficacy of selection at the short versus long-term is positively correlated with synonymous diversity (fig.~\ref{fig:selcoeff-pop-phylo}C), a proxy of effective population size.
    Altogether, populations with large effective population size are under more efficient selection, confirming the prediction of the nearly-neutral theory of evolution.
    As a consequence of increased selection efficacy, mutations in populations with high diversity are mechanically more likely to be deleterious (fig.~S4), especially for mutations predicted already to be deleterious at the phylogenetic scale (fig.~S5-6).

    Finally, we computed the proportion of substitutions in the terminal branches that were predicted to be under positive selection ($\Sphy > 0$).
    To this aim, for each population with polymorphism data available, we reconstructed the ancestral sequences before the last genus split in the tree.
    In these populations, we show that out of all polarized substitutions in the branches, between 22 and 42\% of all substitutions are under $\Sphy > 0$ (table S1).
    This proportion must be compared to the estimated probability of a mutation to be positively selected ($\Spop > 0$), which is between 4.8 and 11.3\%(table S1).
    As a result, these observed substitutions are likely to have been positive selected because they restored the state which corresponded to an optimal state of the population.
    Statistically, genomes are thus involved in a tug-of-war between a large volume deleterious mutations that eventually reach fixation due to drift, and scarce advantageous mutations that are repairing ancestral deleterious substitutions.
    Taking into account that observed substitutions are likely to be due to positive selection that is not adaptive is thus crucial if one seek to estimate the proportion of adaptation while relying on substitutions between close species\cite{mcdonald_adaptative_1991}.
    % However, and surprisingly, a decrease in the proportion of neutral mutation did not translate into a mechanical increase in the proportion of advantageous mutations.
    % Instead, populations with higher diversity have a lower proportion of advantageous mutations (fig.~S7), this effect is also more pronounced for mutations predicted to be advantageous at the phylogenetic scale (red row in fig.~\ref{fig:all-pop-results}C and fig.~S8).
    % This discrepancy can be explained by the fact that populations with larger diversity have already depleted the putatively advantageous mutations, and that only deleterious are remaining possible.
    % In other words, being on the top of a fixed fitness landscape leaves you with only paths going downhill.
    % Altogether, populations with increased diversity are showing signature of increased selection efficiency and are also less likely to generate positively selected mutations.

@@

@@

    Aside from methodological limitations, the mammalian case study might also not be representative of other clades.
    Indeed, our dataset is quite convenient because mammals have relatively small population sizes, which allow large amount of deleterious mutations to be fixed, and thus, there is a lot of opportunities for non-adaptive positive selection to arise.
    It would thus be of great interest to reproduce our experiment with other clades, such as \textit{drosophila} or birds which have higher effective population size.
    It would also be interesting to have access to more shallow but wider phylogenies to increase the resolution of our predictions.
    % Moreover, mammalian are less affected by codon usage

    From a structural biology perspective, we found that proteins are not optimal for their fitness, which has been proved for their kinetics and thermodynamics.
    We argue that mutation-selection models are thus a mandatory tool in evolutionary biology to detect and quantify adaptation since they genuinely take into account the tug-of-war between scarce advantageous mutations likely to reach fixation and a bulk of deleterious mutations eventually reaching fixations due to their sheer mass.
    Indeed, these models can be used as a null model to predict the overall rate of evolution of proteins\cite{spielman_relationship_2015, dosreis_how_2015}.
    A departure from this model indicates that proteins are evolving under a changing fitness landscape\cite{rodrigue_detecting_2017, tamuri_mutationselection_2021} and is a signal of adaptive evolution\cite{rodrigue_bayesian_2021}.

### 2022-05-16 manuscript/supp-mat.tex
Ancestral reconstruction with codon models

    \begin{center}
        \begin{longtable}{|l|l|r|r|r|r|}
            \toprule
            Population                     & Species             & Tajima $\theta$ & $\proba_{obs}[\divAdv]$ & $\PpolyAdv$ & $\proba [ \polyAdv | \divAdv]$ \\
            \midrule
            \endhead
            \midrule
            \multicolumn{6}{r}{{Continued on next page}} \\
            \midrule
            \endfoot

@@

            Diverse (Equus)                & Equus caballus      & $ 0.003$        & $ 0.161$                & $ 0.073$    & $ 0.779$                       \\
            Diverse (Canis)                & Canis familiaris    & $ 0.004$        & $ 0.069$                & $ 0.041$    & $ 0.262$                       \\
            Iran (IRBT)                    & Bos taurus          & $ 0.009$        & $ 0.123$                & $ 0.054$    & $ 0.300$                       \\
            Uganda (UGBT)                  & Bos taurus          & $ 0.010$        & $ 0.139$                & $ 0.060$    & $ 0.779$                       \\
            Australia (AUCH)               & Capra hircus        & $ 0.004$        & $ 0.105$                & $ 0.061$    & $ 0.119$                       \\
            France (FRCH)                  & Capra hircus        & $ 0.004$        & $ 0.105$                & $ 0.060$    & $ 0.059$                       \\
            Iran (IRCA)                    & Capra aegagrus      & $ 0.004$        & $ 0.105$                & $ 0.062$    & $ 0.053$                       \\
            Iran (IRCH)                    & Capra hircus        & $ 0.005$        & $ 0.093$                & $ 0.058$    & $ 0.094$                       \\
            Italy (ITCH)                   & Capra hircus        & $ 0.004$        & $ 0.103$                & $ 0.059$    & $ 0.053$                       \\
            Morocco (MOCH)                 & Capra hircus        & $ 0.005$        & $ 0.077$                & $ 0.057$    & $ 0.045$                       \\
            Iran (IROA)                    & Ovis aries          & $ 0.009$        & $ 0.107$                & $ 0.048$    & $ 0.144$                       \\
            Iran (IROO)                    & Ovis orientalis     & $ 0.010$        & $ 0.110$                & $ 0.050$    & $ 0.177$                       \\
            Iran (IROV)                    & Ovis vignei         & $ 0.009$        & $ 0.127$                & $ 0.049$    & $ 0.252$                       \\
            Various (ISGC)                 & Ovis aries          & $ 0.009$        & $ 0.108$                & $ 0.049$    & $ 0.194$                       \\
            Morocco (MOOA)                 & Ovis aries          & $ 0.009$        & $ 0.086$                & $ 0.045$    & $ 0.144$                       \\
            Barbados                       & Chlorocebus sabaeus & $ 0.004$        & $ 0.104$                & $ 0.072$    & $ 0.484$                       \\
            Central African Republic (CAR) & Chlorocebus sabaeus & $ 0.007$        & $ 0.105$                & $ 0.066$    & $ 0.312$                       \\
            Ethiopia                       & Chlorocebus sabaeus & $ 0.006$        & $ 0.097$                & $ 0.068$    & $ 0.245$                       \\
            Gambia                         & Chlorocebus sabaeus & $ 0.006$        & $ 0.101$                & $ 0.064$    & $ 0.411$                       \\
            Kenya                          & Chlorocebus sabaeus & $ 0.006$        & $ 0.104$                & $ 0.066$    & $ 0.323$                       \\
            Nevis                          & Chlorocebus sabaeus & $ 0.004$        & $ 0.105$                & $ 0.068$    & $ 0.445$                       \\
            South Africa (SA)              & Chlorocebus sabaeus & $ 0.007$        & $ 0.095$                & $ 0.065$    & $ 0.233$                       \\
            Saint Kitts (SK)               & Chlorocebus sabaeus & $ 0.005$        & $ 0.101$                & $ 0.071$    & $ 0.442$                       \\
            Zambia                         & Chlorocebus sabaeus & $ 0.007$        & $ 0.101$                & $ 0.070$    & $ 0.290$                       \\
            African (AFR)                  & Homo sapiens        & $ 0.003$        & $ 0.052$                & $ 0.092$    & $ 0.779$                       \\
            Ad Mixed American (AMR)        & Homo sapiens        & $ 0.002$        & $ 0.055$                & $ 0.087$    & $ 0.779$                       \\
            East Asian (EAS)               & Homo sapiens        & $ 0.002$        & $ 0.051$                & $ 0.084$    & $ 0.779$                       \\
            European (EUR)                 & Homo sapiens        & $ 0.002$        & $ 0.053$                & $ 0.087$    & $ 0.779$                       \\
            South Asian (SAS)              & Homo sapiens        & $ 0.002$        & $ 0.051$                & $ 0.084$    & $ 0.779$                       \\

@@

        \item $\proba_{obs}[\divAdv]$ is the proportion of SNPs observed with a selection coefficient at the phylogenetic scale ($\Sphy$) larger than 1.
        \item $\PpolyAdv $ is the proportion of DFE with a selection coefficient at the population-genetic scale ($\Spop$) larger than 1, estimated for the whole genome.
        \item $\proba [ \polyAdv | \divAdv]$ is the proportion of DFE with a selection coefficient at the population-genetic scale ($\Spop$) larger than 1, estimated of SNPs observed with a selection coefficient at the phylogenetic scale ($\Sphy$) larger than 1.

@@

    \begin{minipage}{0.32\linewidth}
        \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/regression/results.watterson.all_P-Seq0.scatter.pdf}
    \end{minipage}
    \begin{minipage}{0.32\linewidth}
        \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/regression/results.watterson.neg-weak_P-Seq0.scatter.pdf}
    \end{minipage}
    \begin{minipage}{0.32\linewidth}
        \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/regression/results.watterson.pos-weak_P-Seq0.scatter.pdf}
    \end{minipage}

@@

    \begin{minipage}{0.32\linewidth}
        \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/regression/results.watterson.all_P-Sinf0.scatter.pdf}
    \end{minipage}
    \begin{minipage}{0.32\linewidth}
        \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/regression/results.watterson.neg_P-Sinf0.scatter.pdf}
    \end{minipage}
    \begin{minipage}{0.32\linewidth}
        \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/regression/results.watterson.neg-strong_P-Sinf0.scatter.pdf}
    \end{minipage}

@@

    \begin{minipage}{0.32\linewidth}
        \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/regression/results.watterson.all_P-Ssup0.scatter.pdf}
    \end{minipage}
    \begin{minipage}{0.32\linewidth}
        \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/regression/results.watterson.pos_P-Ssup0.scatter.pdf}
    \end{minipage}

>>>>

    \begin{center}
        \begin{longtable}{|l|l|r|r|r|r|r|}
            \toprule
            Population           & Species             & Tajima $\theta_{\pi}$ & $\mathbb{P}_{div}(S > 0)$ & $\mathbb{P}_{obs}[S>0]$ & $\mathbb{P} [ \beta > 0 ]$ & $\mathbb{P} [ \beta > 0  | S>0]$ \\
            \midrule
            \endhead
            \midrule
            \multicolumn{7}{r}{{Continued on next page}} \\
            \midrule
            \endfoot

@@

            Equus c.             & Equus caballus      & $ 0.002$              & $ 0.301$                  & $ 0.243$                & $ 0.113$                   & $ 0.793$                       \\
            Canis f.             & Canis familiaris    & $ 0.003$              & $ 0.421$                  & $ 0.181$                & $ 0.048$                   & $ 0.761$                       \\
            Iran                 & Bos taurus          & $ 0.005$              & $ 0.249$                  & $ 0.264$                & $ 0.098$                   & $ 0.605$                       \\
            Uganda               & Bos taurus          & $ 0.006$              & $ 0.254$                  & $ 0.249$                & $ 0.095$                   & $ 0.630$                       \\
            Australia            & Capra hircus        & $ 0.003$              & $ 0.286$                  & $ 0.265$                & $ 0.096$                   & $ 0.512$                       \\
            France               & Capra hircus        & $ 0.004$              & $ 0.285$                  & $ 0.274$                & $ 0.092$                   & $ 0.529$                       \\
            Iran (C. aegagrus)   & Capra hircus        & $ 0.004$              & $ 0.284$                  & $ 0.270$                & $ 0.095$                   & $ 0.455$                       \\
            Iran                 & Capra hircus        & $ 0.004$              & $ 0.297$                  & $ 0.239$                & $ 0.080$                   & $ 0.500$                       \\
            Italy                & Capra hircus        & $ 0.004$              & $ 0.285$                  & $ 0.265$                & $ 0.087$                   & $ 0.500$                       \\
            Morocco              & Capra hircus        & $ 0.004$              & $ 0.296$                  & $ 0.200$                & $ 0.080$                   & $ 0.509$                       \\
            Iran                 & Ovis aries          & $ 0.008$              & $ 0.229$                  & $ 0.259$                & $ 0.060$                   & $ 0.366$                       \\
            Iran (O. orientalis) & Ovis aries          & $ 0.009$              & $ 0.226$                  & $ 0.272$                & $ 0.067$                   & $ 0.344$                       \\
            Iran (O. vignei)     & Ovis aries          & $ 0.008$              & $ 0.235$                  & $ 0.307$                & $ 0.075$                   & $ 0.464$                       \\
            Various              & Ovis aries          & $ 0.009$              & $ 0.226$                  & $ 0.279$                & $ 0.065$                   & $ 0.378$                       \\
            Morocco              & Ovis aries          & $ 0.008$              & $ 0.225$                  & $ 0.212$                & $ 0.054$                   & $ 0.377$                       \\
            Barbados             & Chlorocebus sabaeus & $ 0.004$              & $ 0.314$                  & $ 0.258$                & $ 0.109$                   & $ 0.670$                       \\
            Central Afr. Rep.    & Chlorocebus sabaeus & $ 0.006$              & $ 0.315$                  & $ 0.264$                & $ 0.094$                   & $ 0.619$                       \\
            Ethiopia             & Chlorocebus sabaeus & $ 0.005$              & $ 0.307$                  & $ 0.252$                & $ 0.107$                   & $ 0.660$                       \\
            Gambia               & Chlorocebus sabaeus & $ 0.005$              & $ 0.303$                  & $ 0.249$                & $ 0.085$                   & $ 0.666$                       \\
            Kenya                & Chlorocebus sabaeus & $ 0.006$              & $ 0.311$                  & $ 0.272$                & $ 0.095$                   & $ 0.602$                       \\
            Nevis                & Chlorocebus sabaeus & $ 0.004$              & $ 0.302$                  & $ 0.252$                & $ 0.102$                   & $ 0.642$                       \\
            South Africa         & Chlorocebus sabaeus & $ 0.007$              & $ 0.312$                  & $ 0.246$                & $ 0.094$                   & $ 0.638$                       \\
            Saint Kitts          & Chlorocebus sabaeus & $ 0.004$              & $ 0.306$                  & $ 0.250$                & $ 0.106$                   & $ 0.664$                       \\
            Zambia               & Chlorocebus sabaeus & $ 0.006$              & $ 0.308$                  & $ 0.261$                & $ 0.103$                   & $ 0.630$                       \\
            African              & Homo sapiens        & $ 0.003$              & $ 0.256$                  & $ 0.141$                & $ 0.103$                   & $ 1.000$                       \\
            Admixed American     & Homo sapiens        & $ 0.002$              & $ 0.247$                  & $ 0.145$                & $ 0.103$                   & $ 0.945$                       \\
            East Asian           & Homo sapiens        & $ 0.002$              & $ 0.241$                  & $ 0.129$                & $ 0.098$                   & $ 0.918$                       \\
            European             & Homo sapiens        & $ 0.002$              & $ 0.254$                  & $ 0.130$                & $ 0.098$                   & $ 0.919$                       \\
            South Asian          & Homo sapiens        & $ 0.002$              & $ 0.246$                  & $ 0.131$                & $ 0.096$                   & $ 0.912$                       \\

@@

        \item $\mathbb{P}_{div}(S > 0)$ is the proportion of substitution in the terminal branch observed with a selection coefficient at the phylogenetic scale ($\Sphy$) larger than 0.
        \item $\mathbb{P}_{obs}[S>0]$ is the proportion of SNPs observed with a predicted selection coefficient at the phylogenetic scale ($\Sphy$) larger than 0.
        \item $\mathbb{P} [ \beta > 0 ]$ is the proportion of DFE with a selection coefficient at the population-genetic scale ($\Spop$) larger than 1, estimated for the whole genome.
        \item $\proba [ \polyAdv | \divAdv]$ is the proportion of DFE with a selection coefficient at the population-genetic scale ($\Spop$) larger than 1, estimated on the subset of SNPs observed with a predicted selection coefficient at the phylogenetic scale ($\Sphy$) larger than 0.

@@

    \begin{minipage}{0.32\linewidth}
        \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/regression/results.watterson.all_P-Seq0.scatter.pdf}
    \end{minipage}
    \begin{minipage}{0.32\linewidth}
        \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/regression/results.watterson.neg-weak_P-Seq0.scatter.pdf}
    \end{minipage}
    \begin{minipage}{0.32\linewidth}
        \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/regression/results.watterson.pos-weak_P-Seq0.scatter.pdf}
    \end{minipage}

@@

    \begin{minipage}{0.32\linewidth}
        \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/regression/results.watterson.all_P-Sinf0.scatter.pdf}
    \end{minipage}
    \begin{minipage}{0.32\linewidth}
        \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/regression/results.watterson.neg_P-Sinf0.scatter.pdf}
    \end{minipage}
    \begin{minipage}{0.32\linewidth}
        \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/regression/results.watterson.neg-strong_P-Sinf0.scatter.pdf}
    \end{minipage}

@@

    \begin{minipage}{0.32\linewidth}
        \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/regression/results.watterson.all_P-Ssup0.scatter.pdf}
    \end{minipage}
    \begin{minipage}{0.32\linewidth}
        \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/regression/results.watterson.pos_P-Ssup0.scatter.pdf}
    \end{minipage}
